NSNEQ_Moon_Example

### 2017-11-08 NSNEQ_Moon_Example.Rmd
Wrote short text box on TOST in R for manuscript

Using the TOSTtwo function in the TOSTER package in R, we can then calculate the TOST by insterting the summary statistics from Moon & Roeder's (2014) data, assuming an aplha of 0.05, and using +/- the SESOI of 0.0625 as our equivalence bounds.

>>>>

We then calculate the TOST for a two-sample Welch’s t-test, assuming an alpha of 0.05 (two-sided), and using +/- the SESOI of 0.0625 as our equivalence bounds.
